%-------------------------
% Resume in Latex
% Author : Anuar Kairulla
% Template: Aras Gungore (MIT License)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Anuar Kairulla} \\ \vspace{5pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+420705974542}{+420 705 974 542}
    $|$
    \faAt \hspace{.5pt} \href{mailto:anuarkairulla@gmail.com}{anuarkairulla@gmail.com}
    $|$
    \faLinkedin \hspace{.5pt} \href{https://linkedin.com/in/anuar-kairulla-4290a6257}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/NnnotAnwar}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} Prague, Czech Republic
\end{center}

%----------- SUMMARY -----------

%----------- SKILLS -----------

\section{Skills}
  \vspace{5pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Languages:}{ JavaScript (ES6+), TypeScript, Python, SQL, HTML5, CSS3} \\ \vspace{4pt}
        \textbf{Technologies:}{ React.js, Tailwind CSS, Vite, Supabase, Vercel, PostgreSQL, Git} \\ \vspace{4pt}
        \textbf{Methodologies:}{ Scrum, Kanban}
    }}
  \resumeSubHeadingListEnd

%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{5pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cloudmaker LLP}{Oct 2021 \textbf{--} Mar 2022}
      {Junior Web Developer}{Kazakhstan}
        \resumeItemListStart
            \resumeItem{Developed and maintained responsive front-end components using vanilla JavaScript, ensuring cross-browser compatibility.}
            \resumeItem{Built a data visualization module by processing database records into a dynamic pivot table and rendering interactive charts to display key business metrics.}
            \resumeItem{Collaborated with the developer team to translate Figma mockups into functional web interfaces.}
            \resumeItem{Participated in daily stand-ups and sprint planning sessions following the Scrum methodology.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Planuj Smeny (Shift Planner)} $|$ \emph{React, Vite, Tailwind CSS, Supabase, Vercel}}{2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developing a full-stack application for employee shift management, enabling users to track working hours and plan schedules.}
            \resumeItem{Building a fast and responsive user interface with React and Tailwind CSS, utilizing Vite for optimized build performance.}
            \resumeItem{Utilizing Supabase as a Backend-as-a-Service (BaaS) to manage relational data via PostgreSQL and implement secure user authentication.}
            \resumeItem{Deployed the application via Vercel, establishing a CI/CD pipeline for automated builds and seamless continuous updates.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {University of Chemistry and Technology (VŠCHT)}{Prague, Czech Republic}
      {B.Sc. in Economics and Management}{Sep 2023 \textbf{--} Jun 2026 (Expected)}
        \resumeItemListStart
            \small{\item{
            \textbf{Relevant Coursework:} Statistics, Microeconomics, Management Fundamentals.
            }}
        \resumeItemListEnd

    \resumeSubheading
      {College of Information Technology}{Kazakhstan}
      {Associate Degree in Software Development}{Graduated 2022}
        \resumeItemListStart
            \small{\item{Focused on core programming principles, database management, and system administration.}}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- LANGUAGES -----------

\section{Languages}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Russian:}{ Native} $|$ 
        \textbf{Kazakh:}{ Native/Bilingual} $|$ 
        \textbf{English:}{ Upper-Intermediate (B2)} $|$ 
        \textbf{Czech:}{ Upper-Intermediate (B2)} 
    }}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}